---
title: 'Assignment A02: TIDYVERSE'
author: Alyssa van de Riet
date: '2021-05-27'
slug: assignment-a02-tidyverse
categories:
  - tidyverse
  - dplyr
tags: []
---

### Within this assignment:
  * One table verbs
  * Two table verbs
  * Pivoting
  * Missing Values
  * Discussion

### Loading Friends_Info Dataset

```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
friends <- read_csv("friends_info.csv")

friends

```

```{r}
Directors <- friends %>%
  select(Episode, `Prod.
code`, `Rating/Share`, `Directed by`) 
  

rename(Directors, `director(s)` = `Directed by`)

gather(Directors, key = `Prod. code`, value = Episode)

```
```{r}
friends %>% 
separate(Rating/Share, c("Rating", "Share"), sep = "/")

friends$Rating <- as.numeric(friends$Rating) 
friends$Share <- as.integer(friends$Share)
```


```{r}
James_Burrows <- friends %>%
  filter(`Directed by` == "James Burrows")
  
James_Burrows %>% summarize(median(Duration))

James_Burrows

Pamela_Fryman <- friends %>%
    filter(`Directed by` == "Pamela Fryman")

Pamela_Fryman
```

```{r}
Burrows_Episodes <- semi_join(James_Burrows, Directors)

Burrows_Episodes
```

### Dropping missing values

## In this section you can see how the Others_Episodes data frame drops from the original 229 episodes to 212 episodes, dropping not only the 15 episodes that Burrows directed, but also 2 rows with had missing values.To determine if any of the episodes directed by Burrows had missing values as well, drop_na() was used. The resulting data set still had 15 rows, indicating that there was no missing information in these rows.  

```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
Others_Episodes <- anti_join(Directors, Burrows_Episodes) %>%
  drop_na()

Others_Episodes

Burrows_Episodes %>% drop_na()

Burrows_Episodes
```

```{r}
rename(friends, Director = `Directed by`, Writers = `Written by`, USviews = `U.S. viewers`, code = `Prod.\ncode`, RatingperShare = `Rating/Share`)

```
## Grouping Data
### Due to the nature of the data within the James Burrows dataset, when grouping the data by Production code there is no change to the order. This is because the production codes are unique identifiers. However, using the order command allows this to happen. 

```{r}
James_Burrows %>% group_by(`Prod.
code`) 

James_Burrows[order(James_Burrows$`Prod.
code`),]
```


